Sound and Automated Synthesis of Digital Controllers for Continuous Plants

### 2017-03-13 slides/presentation.tex
pres

\begin{frame}{Cyber-Physical Systems}
%
\begin{itemize}
\item 
modern controls are implemented with digital microcontrollers, 
embedded within dynamical plants representing physical components 
\end{itemize}

@@

\tool uses counter\-example guided inductive
synthesis to automate the design of digital controllers that are
correct by construction.
%
\end{frame}

\begin{frame}[fragile]{Cyberphysical System}{Continuous Plant and Digital Controller}

@@

\only<4>{
\begin{displaymath}
\label{eq:pulsetf}
\hat{G}(z) = (1-z^{-1})\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\frac{\hat{G}(s)}{s}}\right\rbrace_{t=kT}}\right\rbrace
\end{displaymath}
}

@@

\only<5>{
\begin{equation*}
\label{eq:outputfunctions}
\hat{Y}(z)=\frac{\nu_{1}(z)}{1+\hat{G}(z) \tilde{C}(z)}+\frac{\nu_{2}(z)\hat{G}(z)}{1+\hat{G}(z) \tilde{C}(z)}+\frac{R(z)\hat{G}(z) \tilde{C}(z)}{1+\hat{G}(z) \tilde{C}(z)}
\end{equation*}
}

\uncover<6>{
Common denominator:
$$\hat{G}_n(z) \tilde{C}_n(z)+\hat{G}_d(z) \tilde{C}_d(z)$$
}

>>>>

\begin{frame}{Cyber-Physical Systems (CPS)}

\begin{itemize}
\item 
modern controls are implemented with digital microcontrollers, 
embedded within dynamical plants representing physical components 
\item 
digital control literature: success and limitations 
\end{itemize}

@@

\pause

\begin{itemize}
\item 
use of counter\-example guided inductive synthesis (CEGIS)\\ 
to automate design of sound digital controllers 
\end{itemize}

\begin{frame}[fragile]{CPS Setup: Continuous Plant and Digital Controller}

@@

\only<4>{
\begin{displaymath}
\hat{G}(z) = (1-z^{-1})\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\frac{\hat{G}(s)}{s}}\right\rbrace_{t=kT}}\right\rbrace
\end{displaymath}
}

@@

\only<5>{
\begin{equation*}
\hat{Y}(z) = 
\frac{\hat{G}(z) \tilde{C}(z)}{1+\hat{G}(z) \tilde{C}(z)}R(z) + 
\frac{1}{1+\hat{G}(z) \tilde{C}(z)} \nu_{1}(z) + 
\frac{\hat{G}(z)}{1+\hat{G}(z) \tilde{C}(z)} \nu_{2}(z) 
\end{equation*}
}

\uncover<6>{
Common denominator:
$$\hat{G}_n(z) \tilde{C}_n(z)+\hat{G}_d(z) \tilde{C}_d(z)$$ 
\textcolor{red}{clarify use of tilde C and of hat C }
}
